sdmTMB: an R package for fast, flexible, and user-friendly generalized linear mixed effects models with spatial and spatiotemporal random fields

### 2023-02-14 doc/paper-jss/owls.Rmd
Remove MCMC sdmTMBextra code

More accurate residuals can be generated using MCMC and \pkg{tmbstan}, but this a slower process.
The MCMC-based residuals are randomized quantile residuals where the fixed effects are fixed at their MLE (maximum likelihoood estimate) values and the random effects are sampled with MCMC via \pkg{tmbstan}/\pkg{Stan}.
To calculate these, we have to use a version of our model fit without REML, which we can quickly obtain with the `update()` method.
We would ideally sample with more MCMC samples than this and assess convergence by setting `print_stan_model = TRUE`.
For the purposes of building this appendix quickly, we will not run this code.

```{r stan-resids-owls, eval=FALSE}
fit_ml <- update(fit_owl, reml = FALSE)
mcmc_resids <- residuals(fit_owl,
  type = "mle-mcmc",
  mcmc_iter = 101,
  mcmc_warmup = 100
)
```

>>>>

More accurate residuals can be generated using MCMC and \pkg{tmbstan}, but this a slower process.
The MCMC-based residuals are randomized quantile residuals where the fixed effects are fixed at their MLE (maximum likelihoood estimate) values and the random effects are sampled with MCMC via \pkg{tmbstan}/\pkg{Stan}.
To calculate these, we would have to use a version of our model fit without REML, which we can quickly obtain with the `update()` method.

```{r stan-resids-owls, eval=FALSE}
fit_ml <- update(fit_owl, reml = FALSE)
```

Then, see the [residuals vignette](https://pbs-assess.github.io/sdmTMB/articles/) for examples of how MCMC residuals can be estimated with the \pkg{sdmTMBextra} package.

### 2023-02-14 doc/paper-jss/pcod.Rmd
Remove MCMC sdmTMBextra code

We can inspect randomized quantile residuals calculated with predictions that used the Laplace approximation:

```{r}
set.seed(123)
r <- residuals(fit)
```

Or perhaps better, use MCMC residuals (Fig.\ \ref{fig:mcmc-resids-vis}).

```{r mcmc-resids, warning=FALSE, results='hide', cache=TRUE}
set.seed(123)
post <- sdmTMBextra::predict_mle_mcmc(fit, mcmc_iter = 200, mcmc_warmup = 100)
r <- residuals(fit, mcmc_samples = post, type = "mle-mcmc")
```

```{r mcmc-resids-vis, out.width="4in", fig.cap="MCMC residuals.", fig.pos='ht', fig.align='center'}
qqnorm(r)
qqline(r)
```

>>>>

We can inspect randomized quantile residuals calculated with predictions that used the Laplace approximation (Fig.\ \ref{fig:laplace-resids-vis}):

```{r laplace-resids-vis}
set.seed(123)
r <- residuals(fit)
qqnorm(r)
qqline(r)
```

These residuals can suggest model fit issues even with properly specified models due to the Laplace approximation [@thygesen2017a]. We could instead use MCMC residuals, which more accurate but slower. These are currently available in the \pkg{sdmTMBextra} package at <https://github.com/pbs-assess/sdmTMBextra> and are demonstrated in the [residuals vignette](https://pbs-assess.github.io/sdmTMB/articles/).
